Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control

### 2019-06-18 NFES_Review/article.tex
table completed

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. 
\end{abstract}
\end{frontmatter}
\tableofcontents

@@

\begin{longtable}{p{\dimexpr.1641\linewidth-2\tabcolsep}p{\dimexpr.13800000000000004\linewidth-2\tabcolsep}p{\dimexpr.1634\linewidth-2\tabcolsep}p{\dimexpr.46839999999999996\linewidth-2\tabcolsep}p{\dimexpr.0661\linewidth-2\tabcolsep}}

@@

  \unskip~\cite{527120:11974325}\\

@@

  \unskip~\cite{527120:11974326}\\

@@

  \unskip~\cite{527120:11974327}\\

@@

  \unskip~\cite{527120:11974328}\\

@@

\textbf{Solution Concentration:}

\textbf{Nozzle:}

\textbf{Solution deposition rate:}

\textbf{Nozzle-to-substrate distance:}

\textbf{Substrate composition:}

\textbf{Applied voltage:}

\textbf{x-y stage velocity:}

\textbf{Fiber Diameter:}

\textbf{Distance between adjacent fibers:}

>>>>

\begin{abstract}
Near-field electrospinning (NFES) have demonstrated to be one of the top techniques for the fabrication of nano and micro fibers with accurate spatial control. In the attempt to create  NFES has suffered a number of variations

Lorem ipsum dolor sit amet

One-dimensional (1-D) nanostructures have attracted enormous research interest due to their unique physicochemical properties and wide application potential. These 1-D nanofibers are being increasingly applied to biomedical fields owing to their high surface area-to-volume ratio, high porosity, and the ease of tuning their structures, functionalities, and properties. Many biomedical nanofiber reviews have focused on tissue engineering and drug delivery applications but have very rarely discussed their use as wound dressings. However, nanofibers have enormous potential as wound dressings and other clinical applications that could have wide impacts on the treatment of wounds. Herein, the authors review the main fabrication methods of nanofibers as well as requirements, strategies, and recent applications of nanofibers, and provide perspectives of the challenges and opportunities that face multifunctional nanofibers for active therapeutic applications.

Near field electrospinning is one of the leading techniques in accurate placement of nanofibers. This technique has evolved from using AFM tips to supply a limited volume of solution for electrospinning to nozzle-based system where a continuous stream of solution can be extruded.

The precision and accuracy of the fiber deposition has also vastly improved from simple formation of oriented fibers on a collector to precise deposition of the fiber at a specific point. Despite the progress, several intrinsic limitation or characteristic of near-field electrospinning still needs to be noted when employing this technique.
\end{abstract}
\begin{keyword} 
      polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
\end{keyword}

\end{frontmatter}
\tableofcontents

@@

\begin{longtable}{p{\dimexpr.1641\linewidth-2\tabcolsep}p{\dimexpr.13520000000000005\linewidth-2\tabcolsep}p{\dimexpr.1662\linewidth-2\tabcolsep}p{\dimexpr.46839999999999996\linewidth-2\tabcolsep}p{\dimexpr.0661\linewidth-2\tabcolsep}}

@@

  \unskip~\cite{527120:11974325}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}

@@

  \unskip~\cite{527120:11974326}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}

@@

  \unskip~\cite{527120:11974327}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}

@@

  \unskip~\cite{527120:11974328}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
  Mechano-Electrospinning &
  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless steel nozzle with inner diameter of 160$\mu m $ and outer diameter of 310$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2-5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicone \mbox{}\protect\newline \textbf{Applied voltage:}polymer jet initiated at 2$kV $ and dispensed at 1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 200-400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} from 344$\pm $32 to 214$\pm $27$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
  \unskip~\cite{527120:11974304}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Poly(co-Glycolic) acid (PLGA)  &
  Dimethyl Carbonate (DMC) &
  Tethered Pyro-Electrohydro-dynamic Spinning (TPES) &
  \textbf{Solution Concentration:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
  \unskip~\cite{527120:11974307}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Poly(ethylene oxide) (PEO) with Tetrabutylammonium tetrafluoroborate (TBF) and SU-8 2002 &
  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline \textbf{Nozzle:} needle inner diameter of 533$\mu m $ and outer diameter of 710$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:}\textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:}\textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
  \unskip~\cite{527120:12033655}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
  Water:Ethanol (3:2) &
  Suspension NFES &
  \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} stainless steel needle (25 G) with inner diameter of 0.25$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 3$nL/s $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} between 0.5 and 10$mm $ with 0.5$mm $ increments \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon electrodes \mbox{}\protect\newline \textbf{Applied voltage:} 1.6$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50, 150, and 250$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 0.1 and 0.5$mm $ &
  \unskip~\cite{527120:12033656}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
   &
  \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &
  \unskip~\cite{527120:12033657}\\

@@
